### 2018-08-01 manuscript/manuscript.tex
change default for manuscript to knitr not Sweave and add manuscript

\documentclass{jors}

@@

\usepackage{listings}

\begin{document}

<<echo = FALSE>>=
opts_chunk$set(size = 'footnotesize',
               fig.pos = 'H',
               root.dir = 'manuscript/')
@

@@

<<>>=
library(deconvolve)
head(juncus)
@

@@

<<>>=
deriv_juncus <- process(juncus,
                        temp = 'temp_C',
                        mass = 'mass_loss',
                        init_mass = 18.96)
deriv_juncus
@

@@

<<eval = FALSE>>=
plot(deriv_juncus)
@

<<echo = FALSE, fig.cap = '\\label{Fig:process} Process function output from \\textit{Juncus amabilis} example dataset.', fig.subcap = c('\\label{Fig:massloss} Thermogravimetric mass loss curve.', '\\label{Fig:rateloss} Derivative thermogravimetric rate of mass loss across temperature, scaled by initial mass of sample.'), out.width = '.49\\linewidth', fig.asp = 1, fig.ncol = 2>>=
plot(deriv_juncus, plot_type = 'mass')
plot(deriv_juncus, plot_type = 'rate')
@

@@

<<echo = FALSE, fig.cap = '\\label{Fig:fs_simulation} Parametric examination of Fraser-Suzuki function using simulated data', out.width = '.9\\linewidth', fig.asp = 1>>=
simulate_fraser_suzuki <- function () {

  x <- seq(200, 700)
  h1 <- deconvolve::fs_function(x, 0.004, -0.25, 400, 60)
  h2 <- deconvolve::fs_function(x, 0.006, -0.25, 400, 60)
  h3 <- deconvolve::fs_function(x, 0.008, -0.25, 400, 60)
  h4 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)

  s1 <- deconvolve::fs_function(x, 0.010, -0.55, 400, 60)
  s2 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
  s3 <- deconvolve::fs_function(x, 0.010, 0.25, 400, 60)
  s4 <- deconvolve::fs_function(x, 0.010, 0.55, 400, 60)

  p1 <- deconvolve::fs_function(x, 0.010, -0.25, 350, 60)
  p2 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
  p3 <- deconvolve::fs_function(x, 0.010, -0.25, 450, 60)
  p4 <- deconvolve::fs_function(x, 0.010, -0.25, 500, 60)

  w1 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 30)
  w2 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
  w3 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 90)
  w4 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 120)

  par(oma = c(5, 5, 0, 2), mar = c(1, 3, 2, 0), mfrow = c(2, 2))

  plot(x, h4, type = 'l', lty = 4, xaxt = 'n', yaxt = 'n', cex = 1.6,
       xlab = '',
       ylab = '')
  axis(side = 2, at = c(0, 0.002, 0.004, 0.006, 0.008, 0.010), cex.axis = 1.2,
       labels = c(0, 0.002, 0.004, 0.006, 0.008, 0.010))
  lines(x, h2, lty = 2)
  lines(x, h3, lty = 3)
  lines(x, h1, lty = 1)
  legend('topleft', legend = '(a)', bty = 'n', cex = 1.6)
  legend('topright', legend = c(expression(paste('h = 0.004 C'^'-1')),
                                expression(paste('h = 0.006 C'^'-1')),
                                expression(paste('h = 0.008 C'^'-1')),
                                expression(paste('h = 0.010 C'^'-1')),
                                's = -0.25',
                                'p = 400 C',
                                'w = 60 C'),
         bty = 'n', cex = 1.2,
         lty = c(1, 2, 3, 4, NA, NA, NA)
  )

  plot(x, s1, type = 'l', lty = 1, xaxt = 'n', yaxt = 'n', cex = 1.6,
       xlab = '',
       ylab = '')
  lines(x, s2, lty = 2)
  lines(x, s3, lty = 3)
  lines(x, s4, lty = 4)
  legend('topleft', legend = '(b)', bty = 'n', cex = 1.6)
  legend('topright', legend = c(expression(paste('h = 0.010 C'^'-1')),
                                's = -0.5',
                                's = -0.25',
                                's = 0.25',
                                's = 0.55',
                                'p = 400 C',
                                'w = 60 C'),
         bty = 'n', cex = 1.2,
         lty = c(NA, 1, 2, 3, 4, NA, NA)
  )

  plot(x, p1, type = 'l', lty = 1, xaxt = 'n', yaxt = 'n', cex = 1.6,
       xlab = '',
       ylab = '')
  axis(side = 1, at = c(200, 300, 400, 500, 600, 700), cex.axis = 1.2,
       labels = c(200, 300, 400, 500, 600, 700))
  axis(side = 2, at = c(0, 0.002, 0.004, 0.006, 0.008, 0.010), cex.axis = 1.2,
       labels = c(0, 0.002, 0.004, 0.006, 0.008, 0.010))
  lines(x, p2, lty = 2)
  lines(x, p3, lty = 3)
  lines(x, p4, lty = 4)
  legend('topleft', legend = '(c)', bty = 'n', cex = 1.6)
  legend('topright', legend = c(expression(paste('h = 0.010 C'^'-1')),
                                's = -0.25',
                                'p = 350 C',
                                'p = 400 C',
                                'p = 450 C',
                                'p = 500 C',
                                'w = 60 C'),
         bty = 'n', cex = 1.2,
         lty = c(NA, NA, 1, 2, 3, 4, NA)
  )

  plot(x, w1, type = 'l', lty = 1, xaxt = 'n', yaxt = 'n', cex = 1.6,
       xlab = '',
       ylab = '')
  axis(side = 1, at = c(200, 300, 400, 500, 600, 700), cex.axis = 1.2,
       labels = c(200, 300, 400, 500, 600, 700))
  lines(x, w2, lty = 2)
  lines(x, w3, lty = 3)
  lines(x, w4, lty = 4)
  legend('topleft', legend = '(d)', bty = 'n', cex = 1.6)
  legend('topright', legend = c(expression(paste('h = 0.010 C'^'-1')),
                                's = -0.25',
                                'p = 400 C',
                                'w = 30 C',
                                'w = 60 C',
                                'w = 90 C',
                                'w = 120'),
         bty = 'n', cex = 1.2,
         lty = c(NA, NA, NA, 1, 2, 3, 4))

  mtext(text = 'Temperature (C)',
        side = 1,
        line = 2.1,
        outer = TRUE,
        cex = 1.8)
  mtext(text = expression(paste('Rate of mass loss (-dm/dT) (C'^'-1', ')')),
        side = 2,
        line = 0.9,
        outer = TRUE,
        cex = 1.8)
}
simulate_fraser_suzuki()
@

@@

<<>>=
output_juncus <- deconvolve(deriv_juncus)
output_juncus
@

The output of the \verb|deconvolve| function is a list of five items:
\begin{enumerate}
\item{the data used to fit the function,
<<>>=
DTG_data <- rate_data(output_juncus)
head(DTG_data)
@
}
\item{the upper and lower temperature bounds to which the data were cropped,
<<>>=
temp_bounds(output_juncus)
@

}
\item{the model fit including parameter estimates,
<<eval = FALSE>>=
model_fit(output_juncus)
@

<<echo = FALSE>>=
cat(paste0('Nonlinear regression model\n',
          '  model: deriv ~ fs_mixture(temp_C, height_1, skew_1, position_1,\n',
          '    width_1, height_2, skew_2, position_2, width_2, height_3,\n',
          '    skew_3, position_3, width_3)\n',
          '  data: dataframe\n',
          '  height_1   skew_1     position_1 width_1    height_2   skew_2\n',
          '  3.944e-03  1.258e-01  2.662e+02  5.106e+01  5.793e-03  1.344e-02\n',
          '  position_2 width_2    height_3   skew_3     position_3 width_3\n',
          '  3.173e+02  2.866e+01  1.163e-03  1.085e-01  3.300e+02  2.500e+02\n',
          '  residual sum-of-squares: 9.299e-06\n\n',
          'Number of iterations to convergence: 23\n',
          'Achieved convergence tolerance: 1.49e-08'))
@
}
\item{the number of curves,
<<>>=
output_juncus$n_curves
@
}
\item{and the mean and upper and lower estimates of the weight of each component.
<<>>=
component_weights(output_juncus)
@
}
\end{enumerate}
If you \verb|plot()| the output of the \verb|deconvolve| function you will see the result of the deconvolution (Fig.~\ref{Fig:decon}). This default plot shows the underlying DTG data, the overall mixture model curve, as well as the components curves.

<<fig.cap = '\\label{Fig:decon} Deconvolution of \textit{Juncus amabilis} example dataset. Mass loss data overlaid with output of deconvolution. Rate of mass loss scaled by initial mass of sample.'>>=
plot(output_juncus)
@

>>>>

\documentclass{jors}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

@@

\usepackage{listings}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(deconvolve)}
\hlkwd{head}\hlstd{(juncus)}
\end{alltt}
\begin{verbatim}
##   temp_C mass_loss
## 1 31.453 -0.000931
## 2 31.452 -0.001340
## 3 31.450 -0.001350
## 4 31.450 -0.001660
## 5 31.450 -0.001680
## 6 31.450 -0.001800
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{deriv_juncus} \hlkwb{<-} \hlkwd{process}\hlstd{(juncus,}
                        \hlkwc{temp} \hlstd{=} \hlstr{'temp_C'}\hlstd{,}
                        \hlkwc{mass} \hlstd{=} \hlstr{'mass_loss'}\hlstd{,}
                        \hlkwc{init_mass} \hlstd{=} \hlnum{18.96}\hlstd{)}
\hlstd{deriv_juncus}
\end{alltt}
\begin{verbatim}
## Derivative thermogravimetry data (DTG) calculated for
##  768 datapoints from 31.5 to 798.52 degrees C.
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{plot}\hlstd{(deriv_juncus)}
\end{alltt}
\end{kframe}
\end{knitrout}

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
\subfloat[\label{Fig:massloss} Thermogravimetric mass loss curve.\label{fig:unnamed-chunk-51}]{\includegraphics[width=.49\linewidth]{figure/unnamed-chunk-5-1} }
\subfloat[\label{Fig:rateloss} Derivative thermogravimetric rate of mass loss across temperature, scaled by initial mass of sample.\label{fig:unnamed-chunk-52}]{\includegraphics[width=.49\linewidth]{figure/unnamed-chunk-5-2} }\caption{\label{Fig:process} Process function output from \textit{Juncus amabilis} example dataset.}\label{fig:unnamed-chunk-5}
\end{figure}

\end{knitrout}

@@

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
\includegraphics[width=.9\linewidth]{figure/unnamed-chunk-6-1} \caption{\label{Fig:fs_simulation} Parametric examination of Fraser-Suzuki function using simulated data}\label{fig:unnamed-chunk-6}
\end{figure}

\end{knitrout}

@@

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{output_juncus} \hlkwb{<-} \hlkwd{deconvolve}\hlstd{(deriv_juncus)}
\hlstd{output_juncus}
\end{alltt}
\begin{verbatim}
## Deconvolution by 3-part Fraser-Suzuki mixture model fitted to 
## 580 datapoints from 120 to 700 degrees C.
\end{verbatim}
\end{kframe}
\end{knitrout}

The output of the \verb|deconvolve| function is a list of five items:
\begin{enumerate}
\item{the data used to fit the function,
\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{DTG_data} \hlkwb{<-} \hlkwd{rate_data}\hlstd{(output_juncus)}
\hlkwd{head}\hlstd{(DTG_data)}
\end{alltt}
\begin{verbatim}
##       temp_C        deriv   mass_T
## 5325 120.514 9.570652e-05 17.91630
## 5384 121.501 9.885901e-05 17.91445
## 5445 122.515 1.003878e-04 17.91252
## 5505 123.514 9.133606e-05 17.91079
## 5565 124.513 6.493836e-05 17.90956
## 5625 125.509 8.578618e-05 17.90794
\end{verbatim}
\end{kframe}
\end{knitrout}
}
\item{the upper and lower temperature bounds to which the data were cropped,
\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{temp_bounds}\hlstd{(output_juncus)}
\end{alltt}
\begin{verbatim}
## [1] 120 700
\end{verbatim}
\end{kframe}
\end{knitrout}

}
\item{the model fit including parameter estimates,
\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{model_fit}\hlstd{(output_juncus)}
\end{alltt}
\end{kframe}
\end{knitrout}

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## Nonlinear regression model
##   model: deriv ~ fs_mixture(temp_C, height_1, skew_1, position_1,
##     width_1, height_2, skew_2, position_2, width_2, height_3,
##     skew_3, position_3, width_3)
##   data: dataframe
##   height_1   skew_1     position_1 width_1    height_2   skew_2
##   3.944e-03  1.258e-01  2.662e+02  5.106e+01  5.793e-03  1.344e-02
##   position_2 width_2    height_3   skew_3     position_3 width_3
##   3.173e+02  2.866e+01  1.163e-03  1.085e-01  3.300e+02  2.500e+02
##   residual sum-of-squares: 9.299e-06
## 
## Number of iterations to convergence: 23
## Achieved convergence tolerance: 1.49e-08
\end{verbatim}
\end{kframe}
\end{knitrout}
}
\item{the number of curves,
\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{output_juncus}\hlopt{$}\hlstd{n_curves}
\end{alltt}
\begin{verbatim}
## NULL
\end{verbatim}
\end{kframe}
\end{knitrout}
}
\item{and the mean and upper and lower estimates of the weight of each component.
\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{component_weights}\hlstd{(output_juncus)}
\end{alltt}
\begin{verbatim}
##   HC CL LG value_type
## 1  0  0  0       2.5%
## 2  0  0  0      97.5%
## 3  0  0  0       mean
\end{verbatim}
\end{kframe}
\end{knitrout}
}
\end{enumerate}
If you \verb|plot()| the output of the \verb|deconvolve| function you will see the result of the deconvolution (Fig.~\ref{Fig:decon}). This default plot shows the underlying DTG data, the overall mixture model curve, as well as the components curves.

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{plot}\hlstd{(output_juncus)}
\end{alltt}
\end{kframe}\begin{figure}[H]
\includegraphics[width=\maxwidth]{figure/unnamed-chunk-14-1} \caption{\label{Fig:decon} Deconvolution of 	extit{Juncus amabilis} example dataset. Mass loss data overlaid with output of deconvolution. Rate of mass loss scaled by initial mass of sample.}\label{fig:unnamed-chunk-14}
\end{figure}

\end{knitrout}
